ODGI: scalable tools for pangenome graphs

### 2021-05-31 manuscript/main.tex
5th topic

    \topic{odgi explode, squeeze \& extract} pangenome graphs can embed multiple chromosomes as separated connected
    components (inter-chromosomal structural variants would join the components into bigger ones).
    \cmd{odgi explode} separates the connected components in different \odgi\ format files, while \cmd{odgi squeeze}
    allows merging multiple graphs into the same \odgi\ format file, preventing node ID collisions. \cmd{odgi extract}
    allows extracting specific subregions of the graph as defined by query criteria, thereby simplifying the downstream
    analyses and reducing the resources to work only with the extracted region.

>>>>

    \topic{odgi explode, squeeze \& extract} pangenome graphs can embed multiple chromosomes as separated connected
    components. \cmd{odgi explode} separates them in different files, while \cmd{odgi squeeze} merges
    multiple graphs into the same file, preventing node ID collisions. \cmd{odgi extract} extracts regions of the graph
    as defined by query criteria, thereby reducing the resources to work only with the subgraph.
